Empirical Evaluation of eval in R

### 2020-11-05 inst/analysis/environments.Rmd
Analyze environment for the absolute category

eval_calls <- eval_calls %>% filter(!is.na(envir_expression))
```

@@

```{r envir_list}
eval_calls_env_list <- eval_calls %>% filter(envir_type == "VECSXP")
```

@@

```{r envir_arg_caller}
eval_calls_arg_caller <- eval_calls %>% filter(!is.na(envir_from_arg))
```

@@

In the current dataset, there are no examples of sandbox usage but we should see adistance of 1 in that case.

@@

```{r envir_absolute}
eval_calls_absolute <- eval_calls %>% anti_join(eval_calls_env_list) %>% anti_join(eval_calls_arg_caller)
```

@@

```{r}
eval_calls_absolute <- eval_calls_absolute  %>% add_fake_srcref() %>% group_by(eval_call_srcref) %>%  mutate(envir_distinct = n_distinct(environment_class)) %>% ungroup()
```

>>>>

eval_calls_explicit <- eval_calls %>% filter(!is.na(envir_expression))
```

@@

```{r envir_list}
eval_calls_env_list <- eval_calls_explicit %>% filter(envir_type == "VECSXP")
```

@@

```{r envir_arg_caller}
eval_calls_arg_caller <- eval_calls_explicit %>% filter(!is.na(envir_from_arg))
```

@@

In the current dataset, there are no examples of sandbox usage but we should see a distance of 1 in that case.

@@

```{r envir_absolute}
eval_calls_absolute <- eval_calls_explicit %>% anti_join(eval_calls_env_list) %>% anti_join(eval_calls_arg_caller)
```

@@

```{r}
eval_calls_absolute <- eval_calls_absolute  %>% add_fake_srcref() %>% group_by(eval_call_srcref) %>%  mutate(envir_distinct = n_distinct(environment_class))

eval_calls_absolute %>% ungroup() %>% count(envir_distinct, sort = TRUE)
```

We can also see a few examples:

```{r}
eval_calls_absolute %>% filter(envir_distinct == 2) %>% select(eval_call_expression, environment_class, envir_distinct)
```
